%
% introduction.tex
%
% Copyright (C) 2024 by SpaceLab.
%
% EPS 2.0 Qualification Test Plan
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 4.0
% International License. To view a copy of this license,
% visit http://creativecommons.org/licenses/by-sa/4.0/.
%

%
% \brief Documentation chapter.
%
% \author Ramon de Araujo Borba <ramonborba97@gmail.com>
%
% \version 0.1.0
%
% \date 2024/02/14
%

\chapter{Documentation} \label{ch:documentation}

The documentation for this testing process will follow and adapted version of the documentation structure defined in the ECSS-E-ST-10-02 \cite{ecss-e-st-10-02} and ECSS-E-ST-10-03 \cite{ecss-e-st-10-03}, as recommended in the EPS Test Plan Guidelines.

Three documents are to be generated based on this test plan, and later annexed to this document, resulting in a single instance at the end of the testing process.
These documents are: Test Specifications document, Test Procedures document and Test Reports document.

The Test Specification document describes the detailed specifications and requirements for the tests.
It contains, for each test a description of the purpose of the test, test approach, model to be used, the requirements being verified, required equipment, instrumentation and uncertainties, test conditions and tolerances, pass/fail criteria and related documentation.

The Test Procedures document describes the detailed procedures for execution the tests.
It contains for each test, reference to corresponding TSPE document, description of the item under test configuration,  and detailed step-by-step instructions for the test execution.

The Test Reports document contains the reports for each test. Each report describes the execution of the test, the test results, data analysis and assessments, as well as considerations and conclusions regarding the requirements being verified.

At the end of the testing process, when combining and annexing these documents, it may be of interest to group each test's specification section with the respective procedures and report, for easier reading.